Robust background subtraction in traffic environments

### 2019-02-20 paper/Paper.tex
long period experiments

\subsection{Long Period Experiments}

@@

\begin{figure}[!t]
    \centering
    \subfloat[][Grey]{
        \includegraphics[width=0.45\textwidth]{Figures/grey.png}
    }
    \newline
    \subfloat[][RGB]{
        \includegraphics[width=0.45\textwidth]{Figures/rgb.png}
    }
	\caption{RGB version compared with the Grey one. As we see, there is some difference present but it is negligible}
\end{figure}

@@

\section*{Conclusion}
We have provided a background subtraction system based on the PBAS algorithm. The system is meant to work real time in traffic surveillance scenarios, also under challening environmental conditions and heavy traffic, 24/7. In order to do this, the general purpose PBAS algorithm was studied and the hyperparameters were adapted in order to perform best in this particular scenario. We have validated our work by visual inspection in particular and challenging situations, with long videos with environmental and traffic conditions changing over time. We further experimented with shadow removal methods and we tried to exploit motion informations. Future work can be done in this direction, until arriving to a precise classification of noise and errors in the mask detected. Still, the system as it is now can be employed as a preprocessing step for many anomaly detection applications, such as car accidents, cars going in the wrong direction and people crossing the road.

>>>>

\subsection{Long Period Experiments}
Since our goal is traffic monitoring 24/7, it is important to ensure that the algorithm can adapt as time passes to different light conditions, environmental changes, and traffic intensity variations. In order to do this, we let the algorithm run on ninty minutes long videos recording smooth light transitions (from day to night and viceversa), rough changes of environmental conditions and variations of traffic intensity. Experiments show that the algorithm adapts without any problem in those scenarios. This makes us believe that also in a real 24/7 scenario there wouldn't be any problem of adaptation. However, this behaviour is more than expected: looking at how the PBAS works, we can notice that the state, that is the values of the variables, would change in the same way during the starting iterations as it would after one day of non-stop run.

\begin{figure}[!t]
    \centering
    \subfloat[][00:01:00]{
        \includegraphics[width=0.45\textwidth]{Figures/snow_60.jpg}
    }
    \newline
    \subfloat[][00:26:00]{
        \includegraphics[width=0.45\textwidth]{Figures/snow_1561.jpg}
    }
    \newline
    \subfloat[][00:35:00]{
        \includegraphics[width=0.45\textwidth]{Figures/snow_1921.jpg}
    }
    \newline
    \subfloat[][01:04:00]{
        \includegraphics[width=0.45\textwidth]{Figures/snow_3850.jpg}
    }
    \newline
    \subfloat[][01:29:00]{
        \includegraphics[width=0.45\textwidth]{Figures/snow_5377.jpg}
    }
    \caption{It is shown how the algorithm adapts to change of enviromental conditions. In this case it starts snowing, therefore the road gets dirtier than it was when the video started.}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \subfloat[][Grey]{
        \includegraphics[width=0.45\textwidth]{Figures/grey.png}
    }
    \newline
    \subfloat[][RGB]{
        \includegraphics[width=0.45\textwidth]{Figures/rgb.png}
    }
	\caption{RGB version compared with the Grey one. As we see, there is some difference in the detection accuracy}
\end{figure}

@@

\section*{Conclusion}
We have provided a background subtraction system based on the PBAS algorithm. The system is meant to work real time in traffic surveillance scenarios, also under challening environmental conditions and heavy traffic, 24/7. In order to do this, the general purpose PBAS algorithm was studied and the hyperparameters were adapted in order to perform best in this particular scenario. We have validated our work by visual inspection in particular and challenging situations, with long videos with environmental and traffic conditions changing over time. We further experimented with noise removal methods and we tried to exploit motion informations. Future work can be done in this direction, until arriving to a precise classification of noise and errors in the mask detected. Still, the system as it is now can be employed as a preprocessing step for many anomaly detection applications, such as car accidents, cars going in the wrong direction and people crossing the road.
